Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2024-08-08 paper/main.tex
Updates

In this section, we develop a novel measure of partial association for mixed
data by extending partial correlations \citep{Whittaker2009} \todo{Verify this
citation} to mixed data.
As partial correlations require two things: 1) A
residualization method, and 2) measure of associations between the residuals.
We generalize this to mixed data by combining a mixed data residualization
method \citep{Ankan2023} with a multivariate measure of association based on
Pillai's Trace. Given $ n $ samples $ D = (x, y, \bm{z}) $ of variables $ X $,
$ Y $, and $ \bm{Z} $, we are interested in computing an estimate of the
conditional association $ \rho(X, Y; \bm{Z}) $ between $ X $ and $ Y $
conditioned on $ \bm{Z} $. As the residualization approach requires atleast one
conditional variable to be present, if $ \bm{Z} = \emptyset $, we use a
constant value for $ Z $. Similar to partial correlation, we first compute the
residuals for $ X $ and $ Y $ using $ \bm{Z} $ as the predictor variables. We
use the mixed data residualization approach from \citet{Ankan2023}. Depending
on the type of dependent variable, the residuals are defined as follows:

>>>>

In this section, we develop a novel measure of partial association for mixed
data by extending partial correlations \citep{Whittaker2009} \todo{Verify this
citation} to mixed data. To compute partial correlations we use: 1) A
residualization method, and 2) a measure of associations between the residuals.
In the case of continuous data, the residuals can be computed using a
regression based method and Pearson's correlation coefficient can be used for
computing the association between the residuals. We extend this idea to mixed
data by combining a mixed data residualization method \citep{Ankan2023} with a
multivariate measure of association based, Pillai's Trace \citep{Pillai1955}.
Given $ n $ samples $ D = (x, y, \bm{z}) $ of variables $ X $, $ Y $, and $
\bm{Z} $, we are interested in computing an estimate of the conditional
association $ \rho(X, Y; \bm{Z}) $ between $ X $ and $ Y $ conditioned on $
\bm{Z} $. As the residualization approach requires atleast one conditional
variable to be present, if $ \bm{Z} = \emptyset $, we use a constant value for
$ Z $. Similar to partial correlation, we first compute the residuals for $ X $
and $ Y $ using $ \bm{Z} $ as the predictor variables. We use the mixed data
residualization approach from \citet{Ankan2023}. Depending on the type of
dependent variable, the residuals are defined as follows:
